### 2020-07-10 intro.tex
Add color figure

\subsection{Background}
\begin{figure*}
  \begin{center}
  \includegraphics[width=35pc]{color-palettes.png}\end{center}
  \caption{
  (a) This figure, adapted from the prior work of \citet{Graphite}, 
  shows a Graphite palette associated with the \texttt{Color} class. 
  The client can specify the RGBA components only using literal numbers. 
  (b) A similar Hazel livelit for colors uses live splices for the RGBA components,
  so the client can enter any Hazel expression. 
  In this case, the client has entered a variable, itself defined using a slider livelit, into the RGB 
  splices. The A splice is filled directly with a slider livelit. 
  The color livelit evaluates splices under its closure to display the 
  computed color. 
  The value of \li{defaultColor} is determined by the livelit via a macro expansion step.}
  \label{fig:color}
\end{figure*}

@@

  \item \textbf{Compositionality}: 
  Graphite does not provide any way to {enter subexpressions within a palette}.
  At best, palettes can contain text boxes, but expressions entered into these text boxes 
  do not have any editor support (which creates many problems, one of which is that they cannot themselves be generated by palettes). 
  This implies that palettes can only reasonably generate {closed expressions}. 
  For example, in Figure~\ref{fig:color}(a), the color palette
  is useful only for generating simple color constants. 
  By contrast, livelits have first-class support for subexpressions, which we call \emph{splices} (following
  the terminology of \citet{TLMs} who developed reasoning principles for splicing in a strictly textual setting).
  Fig.~\ref{fig:color}(b) demonstrates splicing: the client is able to define a variable, \li{grayLevel}, 
  to capture the relationship between the red, green, and blue components.
  The client is also able to use a slider inline in the splice governing 
  the alpha (A) component.

>>>>

\subsection{Background}
\begin{figure*}
  \begin{center}
    \begin{subfigure}[t]{0.5\textwidth}
      \centering
      \includegraphics[width=15pc]{slider-color-livelits.png}
    \end{subfigure}\begin{subfigure}[t]{0.5\textwidth}
      \centering
      \includegraphics[width=15pc]{slider-color-livelits.png}
    \end{subfigure}
  \end{center}
  \caption{
  (a) This figure, adapted from the prior work of \citet{Graphite},
  shows a Graphite palette associated with the \texttt{Color} class.
  The client can specify the RGBA components only using literal numbers.
  (b) A similar Hazel livelit for colors uses live splices for the RGBA components,
  so the client can enter any Hazel expression.
  In this case, the client has entered a variable, itself defined using a slider livelit, into the RGB
  splices. The A splice is filled directly with a slider livelit.
  The color livelit evaluates splices under its closure to display the
  computed color.
  The value of \li{default\_color} is determined by the livelit via a macro expansion step.}
  \label{fig:color}
\end{figure*}

@@

  \item \textbf{Compositionality}:
  Graphite does not provide any way to {enter subexpressions within a palette}.
  At best, palettes can contain text boxes, but expressions entered into these text boxes
  do not have any editor support (which creates many problems, one of which is that they cannot themselves be generated by palettes).
  This implies that palettes can only reasonably generate {closed expressions}.
  For example, in Figure~\ref{fig:color}(a), the color palette
  is useful only for generating simple color constants.
  By contrast, livelits have first-class support for subexpressions, which we call \emph{splices} (following
  the terminology of \citet{TLMs} who developed reasoning principles for splicing in a strictly textual setting).
  Fig.~\ref{fig:color}(b) demonstrates splicing: the client is able to define a variable, \li{gray\_level},
  to capture the relationship between the red, green, and blue components.
  The client is also able to use a slider inline in the splice governing
  the alpha (A) component.
